---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# satconcordance

The goal of satconcordance is to make it easy to recode a column of SAT scores into new or old, SAT or ACT scores.

## Overview

This package provides functions to recode SAT scores according to any table in the SAT Concordance Tables (Released 5/9/2016): this includes new SAT to old SAT values, old SAT to new SAT values, new SAT to ACT values, and ACT to new SAT values. All functions call dplyr::recode() to perform optimized recodes. Each function accepts a vector of values, recodes it, and returns the recoded vector.

## Installation

You can install satconcordance from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("capturelabs/satconcordance")
```

## Usage

#### Examples of recoding new scores to old scores:

```{r example}
suppressMessages(require("satconcordance"))
suppressMessages(require("dplyr"))

# Recode new SAT (1600 scale) to old SAT (2400 scale)
new_sat_vals <- round(sample(400:1600, 10), -1)
old_sat_vals <- new_sat_to_old_sat_2400(new_sat_vals)
new_old_vals <- data.frame(new_sat_vals, old_sat_vals)
new_old_vals %>%
     mutate(old_sat_vals_piped = new_sat_to_old_sat_2400(new_sat_vals))

# Recode new SAT (1600 scale) to old SAT (1600 scale)
new_sat_vals <- round(sample(400:1600, 10), -1)
old_sat_vals <- new_sat_to_old_sat_1600(new_sat_vals)
new_old_vals <- data.frame(new_sat_vals, old_sat_vals)
new_old_vals %>%
    mutate(old_sat_vals_piped = new_sat_to_old_sat_1600(new_sat_vals))

# Recode new SAT math section to old SAT math section
new_sat_vals <- round(sample(200:800, 10), -1)
old_sat_vals <- new_sat_math_to_old_sat_math(new_sat_vals)
new_old_vals <- data.frame(new_sat_vals, old_sat_vals)
new_old_vals %>%
    mutate(old_sat_vals_piped = new_sat_math_to_old_sat_math(new_sat_vals))

# Recode new SAT writing and language test to old SAT writing section
new_sat_vals <- sample(10:40, 10)
old_sat_vals <- new_sat_writing_to_old_sat_writing(new_sat_vals)
new_old_vals <- data.frame(new_sat_vals, old_sat_vals)
new_old_vals %>%
    mutate(old_sat_vals_piped = new_sat_writing_to_old_sat_writing(new_sat_vals))

# Recode new SAT reading test to old SAT critical reading section
new_sat_vals <- sample(10:40, 10)
old_sat_vals <- new_sat_reading_to_old_sat_reading(new_sat_vals)
new_old_vals <- data.frame(new_sat_vals, old_sat_vals)
new_old_vals %>%
    mutate(old_sat_vals_piped = new_sat_reading_to_old_sat_reading(new_sat_vals))

# Recode new SAT EBRW section to old SAT writing plus critical reading sections
new_sat_vals <- round(sample(200:800, 10), -1)
old_sat_vals <- new_sat_ebrw_to_old_writingreading(new_sat_vals)
new_old_vals <- data.frame(new_sat_vals, old_sat_vals)
new_old_vals %>%
    mutate(old_sat_vals_piped = new_sat_ebrw_to_old_writingreading(new_sat_vals))

# Recode new SAT (1600 scale) to ACT
new_sat_vals <- round(sample(560:1600, 10), -1)
act_vals <- new_sat_to_act(new_sat_vals)
new_act_vals <- data.frame(new_sat_vals, act_vals)
new_act_vals %>%
    mutate(act_vals_piped = new_sat_to_act(new_sat_vals))

# Recode new SAT writing and language section to ACT Enlish/Writing test
new_sat_vals <- sample(17:40, 10)
act_vals <- new_sat_writing_to_act_english(new_sat_vals)
new_act_vals <- data.frame(new_sat_vals, act_vals)
new_act_vals %>%
    mutate(act_vals_piped = new_sat_to_act(new_sat_vals))
```


#### Examples of recoding old scores to new scores:

```{r usage}
suppressMessages(require("satconcordance"))
suppressMessages(require("dplyr"))

# Recode old SAT (2400 scale) to new SAT (1600 scale)
old_sat_vals <- round(sample(600:2400, 10), -1)
new_sat_vals <- old_sat_to_new_sat_2400(old_sat_vals)
old_new_vals <- data.frame(old_sat_vals, new_sat_vals)
old_new_vals %>%
    mutate(new_sat_vals_piped = old_sat_to_new_sat_2400(old_sat_vals))

# Recode old SAT (1600 scale) to new SAT (1600 scale)
old_sat_vals <- round(sample(400:1600, 10), -1)
new_sat_vals <- old_sat_to_new_sat_1600(old_sat_vals)
old_new_vals <- data.frame(old_sat_vals, new_sat_vals)
old_new_vals %>%
    mutate(new_sat_vals_piped = old_sat_to_new_sat_1600(old_sat_vals))

# Recode old SAT writing plus critical reading sections to new SAT EBRW section
old_sat_vals <- round(sample(400:1600, 10), -1)
new_sat_vals <- old_sat_writingreading_to_new_ebrw(old_sat_vals)
old_new_vals <- data.frame(old_sat_vals, new_sat_vals)
old_new_vals %>%
   mutate(new_sat_vals_piped = old_sat_writingreading_to_new_ebrw(old_sat_vals))

# Recode old SAT math section to new SAT math section (200-800 scale)
old_sat_vals <- round(sample(200:800, 10), -1)
new_sat_vals <- old_sat_math_to_new_sat_math_section(old_sat_vals)
old_new_vals <- data.frame(old_sat_vals, new_sat_vals)
old_new_vals %>%
    mutate(new_sat_vals_piped = old_sat_math_to_new_sat_math_section(old_sat_vals))

# Recode old SAT math section to new SAT math test (10-40 scale)
old_sat_vals <- round(sample(200:800, 10), -1)
new_sat_vals <- old_sat_math_to_new_sat_math_test(old_sat_vals)
old_new_vals <- data.frame(old_sat_vals, new_sat_vals)
old_new_vals %>%
   mutate(new_sat_vals_piped = old_sat_math_to_new_sat_math_test(old_sat_vals))

# Recode old SAT writing test to new SAT writing and language section
old_sat_vals <- round(sample(200:800, 10), -1)
new_sat_vals <- old_sat_writing_to_new_sat_writing(old_sat_vals)
old_new_vals <- data.frame(old_sat_vals, new_sat_vals)
old_new_vals %>%
   mutate(new_sat_vals_piped = old_sat_writing_to_new_sat_writing(old_sat_vals))

# Recode old SAT critical reading test to new SAT reading section
old_sat_vals <- round(sample(200:800, 10), -1)
new_sat_vals <- old_sat_reading_to_new_sat_reading(old_sat_vals)
old_new_vals <- data.frame(old_sat_vals, new_sat_vals)
old_new_vals %>%
   mutate(new_sat_vals_piped = old_sat_reading_to_new_sat_reading(old_sat_vals))

# Recode ACT to new SAT (1600 scale)
act_vals <- sample(11:36, 10)
new_sat_vals <- act_to_new_sat(act_vals)
act_new_vals <- data.frame(act_vals, new_sat_vals)
act_new_vals %>%
   mutate(new_sat_vals_piped = act_to_new_sat(act_vals))

# Recode ACT Enlish/Writing test to new SAT writing and language section
act_vals <- sample(11:36, 10)
new_sat_vals <- act_english_to_new_sat_writing(act_vals)
act_new_vals <- data.frame(act_vals, new_sat_vals)
act_new_vals %>%
    mutate(new_sat_vals_piped = act_english_to_new_sat_writing(act_vals))

```
