---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# satconcordance

The goal of satconcordance is to make it easy to recode a column of SAT scores into new or old, SAT or ACT scores.

## Overview

This package provides functions to recode scores according to any table in the SAT Concordance Tables (Released 5/9/2016): this includes new SAT to old SAT values, old SAT to new SAT values, new SAT to ACT values, and ACT to new SAT values. All functions call dplyr::recode() to perform optimized recodes. Each function accepts a vector of values, recodes it, and returns the recoded vector.

## Installation

You can install satconcordance from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("capturelabs/satconcordance")
```

## Example

This is a basic example which shows you how to recode old SAT values on a 2400 scale to new SAT values on a 1600 scale:

```{r example}
suppressMessages(require("satconcordance"))
suppressMessages(require("dplyr"))

# generate example vector
old_sat_vals <- round(sample(600:2400, 10), -1)

# recode old SAT values to new SAT values
new_sat_vals <- old_sat_to_new_sat_2400(old_sat_vals)

# assemble old and new SAT values in data.frame and visually compare
old_new_vals <- data.frame(old_sat_vals, new_sat_vals)
print(old_new_vals)

# recode old SAT values to new SAT values in dplyr::mutate() pipeline
old_new_vals %>%
  mutate(new_sat_vals_piped = old_sat_to_new_sat_2400(old_sat_vals))

```
